---
title: "Data wrangling and tidying with the Tidyverse"
date: "`r Sys.Date()`"
author: "___"
output: 
  html_document:
    fig_width: 6
    fig_height: 5
    toc: true
    toc_float: true
---

```{r setup}
library(tidyverse)

bookings <- read_csv("bookings.csv")
properties <- read_csv("properties.csv")
```

## Task 1 - Base R vs. dplyr

Create a new tibble `x` that

- only contains the columns `room_nights` and `review_score`, and
- only contains the bookings with a price per night of less than 80.

1. ...using base `R` functions only, i.e., without using `dplyr` functions.
2. ...using the `dplyr` functions `select()` and `filter()`.

```{r 1}
# base R
x <- bookings[_____ < 80, c("room_nights", "review_score")]
x

# tidyverse
x <- filter(bookings, _____ < 80)
x <- select(x, _____, _____)
x
```

## Task 2 - Pipelines

Use `%>%` to write a pipeline which extracts all bookings with Friday as check-in
day while only returning the columns `property_id` and `status`.

```{r 2}
bookings %>%
  filter(_____ == "fri") %>%
  select(_____, _____)
```

## Task 3 - `mutate()`

Write a pipeline which calculates the mean-centered `price_per_night`. 
Name the new column `centered_ppn`. 
The returned data frame should only contain this new column.

```{r 3}
bookings %>% 
  _____(_____ = price_per_night - mean(price_per_night)) %>%
  select(centered_ppn) # only return new column
```

## Task 4 - `summary()`

Obtain a one-row summary data frame of `bookings` containing the following statistics:

- The number of rows (Hint: use the function `n()`)
- The number of `"stayed"` bookings
- The mean of the _total price_ (Hint: you have to compute the total price first)

The output tibble should contain three columns and just one row.

```{r 4}
bookings %>%
  mutate(total_price = _____ * _____) %>%
  summarize(
    n = _____,
    n_stayed = _____,
    mean_price = _____
  )
```

## Task 5 - `group_by()` + `summarize()`

Write a pipeline that returns only the most expensive booking of each property. 
Select only the columns `property_id` and total price.

You should get as many rows as there are unique properties:

```{r 5-n_distinct}
n_distinct(bookings$property_id) # convenience function for `length(unique(bookings$property_id))`
```

Recommended approach:

1. Calculate `price_total` using `mutate()`.
2. Group by `property_id` using `group_by()`.
3. Filter rows where the total price is equal to the maximum of the total price
(for that property using `filter()`).
4. Select the columns `property_id` and `price_total` using `select()`.

```{r 5}
bookings %>%
  mutate(price_total = _____ * _____) %>%
  group_by(_____) %>%
  arrange(desc(price_total)) %>%
  slice(_____) %>% # guarantees that exactly one row is returned for each property
  select(_____, _____)
```

## Task 6 - `*_join` functions

Calculate the number of bookings per city.

Hint: Join the tibbles `bookings` and `properties` and _count_ the number of rows per city.

```{r 6}
bookings %>%
  _____(properties, by = "property_id") %>%
  _____(destination)
```

## Task 7 - `pivot_*` functions

_Do properties appeal to business travelers and tourists alike?_

- Convert the column `for_business` to a factor with the levels `"business"` and `"tourist"`.
- For each property and for business travelers and tourists separately, calculate the average review score.
- Then, calculate the average review score difference between business travelers and tourists.

```{r 7}
bookings %>%
  _____(for_business = factor(for_business, labels = c("business", "tourist"))) %>%
  _____(property_id, for_business) %>%
  _____(avg_review_score = mean(review_score, na.rm = TRUE)) %>%
  ungroup() %>%
  pivot_wider(names_from = _____, values_from = _____) %>%
  mutate(diff = business - tourist) %>%
  _____(avg_diff = mean(diff, na.rm = TRUE))
```
