---
title: "The R language: Vectors, Classes, Functions, Iteration"
date: "`r Sys.Date()`"
author: "___"
output: 
  html_document:
    fig_width: 6
    fig_height: 5
    toc: true
    toc_float: true
---

```{r setup}
library(tidyverse)
library(lubridate)

data(attrition, package = "modeldata")
attrition <- as_tibble(attrition)
```

## Functions

Write your own standard deviation function without using `mean()`, `var()` and `sd()`.

```{r}

```


Write a greeting function that takes two arguments, a time and a name, and says "good morning <name>", "good afternoon <name>", or "good evening <name>", depending on the time of day. 
Use `lubridate::now()` as default for the time argument.

```{r}

greet(name = "Uli")
#> [1] "good afternoon Uli"
greet(ymd_h("2021-03-31 05"), "Bob")
#> [1] "good morning Bob"
greet(ymd_h("2021-03-31 13"), "Alice")
#> [1] "good afternoon Alice"
greet(ymd_h("2021-03-31 20"), "Cedric")
#> [1] "good evening Cedric"
```


## Iteration

Use a map function to check for each column of `attrition` whether it is a factor.

```{r attrition-is-factor}

```

Use a map function to extract the type of each column in `attrition`.

```{r}

```

Using a map function, write a pipeline which returns the number of distinct values for each factor column in `attrition`. (Hint: you can select columns based on a logical condition using `keep()`).

```{r}

```

Simplify the following code using `map_dfr()`.

```{r}
setosa <- read_csv("iris-setosa.csv") %>%
  mutate(Species = "setosa")
versicolor <- read_csv("iris-versicolor.csv") %>%
  mutate(Species = "versicolor")
virginica <- read_csv("iris-virginica.csv") %>%
  mutate(Species = "virginica")
df_iris <- bind_rows(setosa, versicolor, virginica)
df_iris
```

```{r}
species <- c("setosa", "versicolor", "virginica")
map_dfr(_____)
```

Complete the following pipeline to create an age histogram for each Department. 
Set the number of histogram bins to 12.

```{r}
attrition %>%
  nest(data = _____) %>%
  mutate(gg = _____(data, ~ _____)) %>%
  pull(gg)
```

The code below builds a linear regression model for the relationship between age and monthly income for each department in the attrition data. 
Use a map function to add a column `r_squared` by extracting the real-valued `r.squared` element from `lm_summary` which quantifies goodness of the fit. (See `?lm.summary`)

```{r}
attrition %>%
  group_by(_____) %>%
  _____(lm_summary = list(summary(lm(MonthlyIncome ~ Age)))) %>%
  mutate(r_squared = _____(lm_summary, "r.squared"))
```


