---
title: "Predictors of child aggression"
date: "`r Sys.Date()`"
author: "___"
output: 
  html_document:
    fig_width: 6
    fig_height: 5
    toc: true
    toc_float: true
---

In this exercise, we examine the relationship between aggression and several potentially predictive factors in 666 children. 

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
cha <- read_csv("child_aggression.csv")
```

The 6 variables in the data are:

- `aggression`: the higher the score, the more aggression has been observed in the child,
- `tv`: the higher the score, the more time spent watching TV,
- `video_games`: the higher the score, the more time spent playing video games,
- `sibling_aggression`: the higher the score, the more aggression has been observed in their older sibling.
- `diet`: the higher the score, the better the diet,
- `parenting_style`: the higher the score, the worse the parenting practices,

## Task 1

Before we actually build regression models, we explore the variables of the data: 

a. Print a summary of the data frame. Explain what a value of `tv` = 0 means in simple terms.
b. Create a histogram for each variable. Tip: Use `facet_wrap()`
c. Create a scatterplot for `parenting_style` vs. `tv`. Describe the bivariate relationship in terms of 
    - linearity
    - direction
    - strength
    - outliers

(Just qualitatively, without using any measures.)

```{r 1a}

```

```{r 1b, fig.width=8}
cha %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>%
ggplot(aes(_____)) +
  geom______() +
  _____(~ _____)
```


```{r 1c}
ggplot(cha, aes(x = _____, y = _____)) +
  geom_____(alpha = .75)
```

## Task 2

a. Create a correlation matrix (using Pearson correlation). 
b. Interpret the coefficients between `aggression` and each of the other variables.
c. For simple linear regression, the square of the Pearson correlation coefficient equals the coefficient of determination, i.e., $\rho^2 = R^2$. How much variability of `aggression` is explained by the explanatory variable that yields highest $R^2$?

```{r 2-a}
cor_df <- corrr::correlate(_____) # output as data frame
cor_df
```

```{r 2-b}
cor_df %>%
  select(term, aggression) %>%
  arrange(desc(aggression))
```

```{r 2-c}
cor_df %>%
  select(term, aggression) %>%
  arrange(desc(aggression)) %>%
  mutate(r_squared = _____)
```

## Task 3

Create a multiple linear regression model $M_1$ with `aggression` as response and `parenting_style` and `sibling_aggression` as explanatory variables.
Interpret each of the three model coefficients.

```{r 3}
m1 <- _____() %>%
  set_engine(_____) %>%
  fit(_____ ~ _____ + _____, data = _____) 
m1 %>% tidy()
```

## Task 4

Create a multiple linear regression model $M_2$ with `aggression` as response and all other variables as explanatory variables.
Which predictor is most important? Which is least important?

```{r 4}
m2 <- _____() %>%
  set_engine(_____) %>%
  fit(_____ ~ _____, data = _____) 
m2 %>% tidy()
```
  
## Task 5

Compare $M_1$ and $M_2$ with respect to $R^2$ and Adjusted $R^2$. 
Which of the two models should we select?

```{r 5}
m1 %>% _____() 
m2 %>% _____() 
```

## Task 6

Consider Occam's razor for model selection and look again at $M_2$. 

a. Create a new linear regression model $M_3$, but include only those variables which are significant according a confidence level $\alpha$=0.05. 
In other words, remove the variable(s) from the regression equation with `p.value` > 0.05 in $M_2$. 
b. Compare $M_2$ and $M_3$ with respect to Adjusted $R^2$. 

```{r 6-a}
m3 <- _____() %>%
  set_engine(_____) %>%
  fit(_____ ~ _____, data = _____ %>% select(_____)) 
m3 %>% tidy()
```

```{r 6-b}
m2 %>% glance()
m3 %>% glance()
```

## Task 7

For $M_2$ and each predictor, create a scatterplot with the predictor on the x-axis and `aggression` on the y-axis with Cook's distance as point color. Discuss whether some of the points with high Cook's distance have to be removed before generating the regression models.

Repeat this for Leverage (hat values) and residuals.

```{r 7}
augmented_model <- augment(m2$fit, cha)
augmented_model
augmented_model %>%
  pivot_longer(cols = tv:parenting_style) %>%
  ggplot(aes(_____, _____)) +
  geom_point(aes(color = _____), alpha = 0.5) +
  facet_wrap(~ _____, scales = "free_x") +
  scale_color_viridis_c(option = "inferno", direction = -1) 
```

## Task 8

For the second model, how many observations have a standardized residuum of greater than 2 or smaller than -2?

```{r}
augmented_model %>%
  filter(_____) %>%
  nrow()
```

## Task 9 (Stretch)

Explain what the following code does. Compare the model this code chunk builds with $M_2$.

```{r lasso, eval = FALSE}
wf <- workflow() %>%
  add_model(
    linear_reg(mixture = 1, penalty = tune()) %>% 
      set_engine("glmnet")
  ) %>%
  add_formula(aggression ~ .)

tune_penalty <- wf %>%
  tune_grid(resamples = vfold_cv(cha, v = 5),
            grid = tibble(penalty = seq(0.1, 1e-20, length.out = 20)))
opt_penalty <- tune_penalty %>% select_best(metric = "rmse")
opt_penalty

wf_final <- wf %>% finalize_workflow(opt_penalty)
wf_final

wf_final %>%
  fit(data = cha) %>%
  tidy()
```


------

Dataset `cha.csv` adapted from: Andy Field, Jeremy Miles, and Zoë Field. [Discovering Statistics Using R](https://studysites.uk.sagepub.com/dsur/main.htm). SAGE Publications, 2012.